### 2021-05-25 paper/paper.tex

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{amsmath, enumitem, url}
\usepackage{xcolor}

% For figures.
% Package float, adds the H option which forces figure placement.
\usepackage{graphicx, float}
\graphicspath{ {./figures/} }

\newcommand\todo{\textcolor{red}{\textbf{[TODO:] }}}

\title{CSE571 Project 2}
\author{Group: Dropouts}
\date{June 2021}

\begin{document}
\maketitle

\section{Group Information}

Members:
\begin{itemize}
    \item Keyan Pishdadian (keyanp@cs.washington.edu)
    \item Jakub Filipek (balbok@cs.washington.edu)
    \item Kyle Deeds (kdeeds@cs.washington.edu)
\end{itemize}

\noindent Source code for behavior cloning approach:
\newline
\url{https://github.com/keyan/duckiebot_behavior_cloning}

\noindent Source code for reinforcement learning approach:
\newline
\url{https://github.com/balbok0/cse571-sp21-project-2-dropouts}

\section{Task Overview}

\todo Reproducing RL research usually doesn't work: https://arxiv.org/abs/1709.06560

\section{Environment Setup}
\subsection{Simulation}
\todo Discuss gym-duckietown and AIDO submissions

\subsection{Real World}
\todo Show different maps used

% \begin{figure}[H]
% \includegraphics[width=8cm,keepaspectratio]{map_simple_loop}
% \centering
% \caption{Photo of physical layout of map 1.}
% \label{fig:map_simple_loop}
% \end{figure}

\section{Reinforcement Learning Approach}
\todo Discuss our initial approach using RL

\todo how we anticipated this would work

\todo ultimately how it performed poorly

\subsection{DQN}
\todo Discuss general algorithmic idea behind DQN

\todo Show training results using DQN and videos of simulator performance

\subsection{DDPG}
\todo Discuss general algorithmic idea behind DDPG

\todo Show training results using DDPG and videos of simulator performance

\section{Behavior Cloning Approach}
\todo High level overview of behavior cloning and end-to-end control with monocular images

\subsection{Data Preparation}
\todo Discuss data collection procedure and cleaning

\todo Discuss final datasets used

\subsection{Model Architectures}
\todo Discuss each model architecture evaluted

\todo Show data from training

\section{Performance Evaluation}
\subsection{Simulator and AIDO}
\todo Share links to videos from simulator and AIDO submissions

\todo Discuss quantative performance for each model including baseline

\subsection{Real World}

\todo Discuss quantative performance for each model including baseline

\todo Share links to videos for each map/model evaluated

\section{Potential Future Improvements}

\todo Discuss algorithmic enhancements

\todo Discuss robot limitations

\bibliographystyle{alpha}
\bibliography{paper}

\end{document}

### 2021-05-25 aido_submission/v0/solution.py
Added trained models to aido submission + naming adjustment

@@ -37,7 +37,8 @@ class Agent:
         model = Modelv0()
         model.load_state_dict(
             torch.load(
-                'modelv0_maserati_plus_simulated.pth',
+                "modelv0_maserati_bill_simulated_amadobot_base.pth",
+                # 'modelv0_maserati_plus_simulated.pth',
                 map_location=self.device,
         ))
         model.eval()

### 2021-05-25 aido_submission/v1/solution.py

@@ -37,7 +37,8 @@ class Agent:
         model = Modelv1()
         model.load_state_dict(
             torch.load(
-                'modelv1_maserati_plus_simulated.pth',
+                "modelv1_maserati_bill_simulated_amadobot_base.pth",
+                # 'modelv1_maserati_plus_simulated.pth',
                 map_location=self.device,
         ))
         model.eval()

### 2021-05-25 model_training/train.py
Fix training for dropout

@@ -144,6 +144,7 @@ def train(args):
         ########################################################################
         # Training
         ########################################################################
+        model.train()
         training_loss = 0.0
         num_correct_pred_lin = torch.tensor(0).to(device)
         num_correct_pred_ang = torch.tensor(0).to(device)
@@ -180,6 +181,7 @@ def train(args):
         ########################################################################
         # Validation
         ########################################################################
+        model.eval()
         validation_loss = 0.0
         num_correct_pred_lin = torch.tensor(0).to(device)
         num_correct_pred_ang = torch.tensor(0).to(device)

### 2021-05-27 model_training/train_nvidia.py
Add low RAM support for training

@@ -27,25 +27,6 @@ DEFAULT_SAVE_NAME = 'saved_nvidia_model'
 PCT_CLOSE = 0.05
 
 
-class VelDataset(Dataset):
-    def __init__(self, observations, lin_velocities, ang_velocities):
-        self.observations = torch.from_numpy(observations).float()
-        self.lin_velocities = torch.from_numpy(lin_velocities).float()
-        self.ang_velocities = torch.from_numpy(ang_velocities).float()
-
-    def __len__(self):
-        return len(self.observations)
-
-    def __getitem__(self, idx):
-        sample = {
-            'image': self.observations[idx],
-            'lin_vel': self.lin_velocities[idx],
-            'ang_vel': self.ang_velocities[idx],
-        }
-
-        return sample
-
-
 def parse_args():
     parser = argparse.ArgumentParser(description='Training Setup')
 
@@ -66,6 +47,11 @@ def parse_args():
         '--split',
         help='Set the training and test split point (input the percentage of training)',
         default=TRAIN_PERCENT, type=float,
+    )
+    parser.add_argument(
+        '--using_colab',
+        help='Uses different settings to account for fewer system resources',
+        action='store_true', default=False,
     )
 
     return parser.parse_args()
@@ -235,4 +221,47 @@ def train(args):
 
 if __name__ == '__main__':
     args = parse_args()
+
+    # On Colab there isn't enough RAM to convert the torch tensors to floats because
+    # this reallocates memory. So here we convert to torch tensors but only convert
+    # to floats get getting items.
+    if args.using_colab:
+        class VelDataset(Dataset):
+            def __init__(self, observations, lin_velocities, ang_velocities):
+                self.observations = torch.from_numpy(observations)
+                self.lin_velocities = torch.from_numpy(lin_velocities)
+                self.ang_velocities = torch.from_numpy(ang_velocities)
+
+            def __len__(self):
+                return len(self.observations)
+
+            def __getitem__(self, idx):
+                sample = {
+                    'image': self.observations[idx].float(),
+                    'lin_vel': self.lin_velocities[idx].float(),
+                    'ang_vel': self.ang_velocities[idx].float(),
+                }
+
+                return sample
+    else:
+        # When we have enough RAM, training is faster when we do the float
+        # conversion just once when loading the dataset.
+        class VelDataset(Dataset):
+            def __init__(self, observations, lin_velocities, ang_velocities):
+                self.observations = torch.from_numpy(observations).float()
[…]

### 2021-05-27 paper/data/tensorboard_to_plot.py
Fix plot title mixup

@@ -25,13 +25,12 @@ def plot(params):
 
     tag_groups = [
         ('Loss', ['Loss/train', 'Loss/validation']),
-        ('Angular Accuracy', ['Accuracy/train/linear', 'Accuracy/validation/linear']),
-        ('Linear Accuracy', ['Accuracy/train/angular', 'Accuracy/validation/angular']),
+        ('Linear Accuracy', ['Accuracy/train/linear', 'Accuracy/validation/linear']),
+        ('Angular Accuracy', ['Accuracy/train/angular', 'Accuracy/validation/angular']),
     ]
     # for tags in scalar_list:
     for title, tags in tag_groups:
         for tag in tags:
-            import pdb; pdb.set_trace()
             x = [int(s.step) for s in acc.Scalars(tag)]
             y = [s.value for s in acc.Scalars(tag)]
             color = BLUE if 'train' in tag else ORANGE

### 2021-05-28 fetch_training_data.sh
Add links to download custom data in fetch_training_data.sh

@@ -1,8 +1,30 @@
-# Fetches the current best dataset, a mix of simulated and real robot images, about 5000 frames.
-wget https://www.dropbox.com/s/ztari0lwvz51cbd/simulated_plus_maserati.log?dl=1 -O simulated_plus_maserati.log
+read -r -p "Download original datasets? [y/N] " response
+case "$response" in
+  [yY])
+    # Fetches the current best dataset, a mix of simulated and real robot images, about 5000 frames.
+    wget https://www.dropbox.com/s/ztari0lwvz51cbd/simulated_plus_maserati.log?dl=1 -O simulated_plus_maserati.log
 
-# This is a very small dataset which is good for testing new models locally for syntax errors/etc.
-wget https://www.dropbox.com/s/03zlt4m4ug5nx4r/sim_small_plus_tori.log?dl=1 -O sim_small_plus_tori.log
+    # This is a very small dataset which is good for testing new models locally for syntax errors/etc.
+    wget https://www.dropbox.com/s/03zlt4m4ug5nx4r/sim_small_plus_tori.log?dl=1 -O sim_small_plus_tori.log
 
-# huge dataset, mostly simulated data
-wget https://www.dropbox.com/s/ms75dkdin6xr89x/maserati_bill_simulated_amadobot_base.log?dl=1 -O maserati_bill_simulated_amadobot_base.log
+    # huge dataset, mostly simulated data
+    wget https://www.dropbox.com/s/ms75dkdin6xr89x/maserati_bill_simulated_amadobot_base.log?dl=1 -O maserati_bill_simulated_amadobot_base.log
+    ;;
+  *)
+    ;;
+esac
+
+read -r -p "Download custom robot datasets? [y/N] " response
+case "$response" in
+  [yY])
+    # Custom dataset recorded using human driver on Keyan's robot. Includes data from traveling
+    # in counter-clockwise direction on the track only.
+    wget https://www.dropbox.com/s/6j99x9wqe6qtjb4/alfredo_ccw.log?dl=1 -O alfredo_ccw.log
+
+    # Custom dataset recorded using human driver on Keyan's robot. Same as above dataset but also
+    # includes data from driving clockwise direction on the track.
+    wget https://www.dropbox.com/s/444pr9dusd74n54/alfredo_ccw_plus_cw.log?dl=1 -O alfredo_ccw_plus_cw.log
+    ;;
+  *)
+    ;;
+esac

### 2021-05-29 paper/paper.tex
Add in-progress draft and figures

@@
 \usepackage{xcolor}
+\usepackage[margin=1in]{geometry}
 
@@
 % Package float, adds the H option which forces figure placement.
-\usepackage{graphicx, float}
+% \usepackage[demo]{graphicx}
+\usepackage{graphicx, float, subfig}
 \graphicspath{ {./figures/} }
@@
 
-\title{CSE571 Project 2}
+\title{Learning end-to-end control for duckiebot driving}
 \author{Group: Dropouts}
@@
 
-\todo Reproducing RL research usually doesn't work: https://arxiv.org/abs/1709.06560
+In this project we sought to explore methods for learning an end-to-end control policy that would allow the duckiebot to navigate tracks autonomously.
+Our goal was to enable the duckiebot and have it make a full loop around a track without any major driving infractions, using only monocular camera data.
+Ideally this system would be robust enough to generalize to new tracks and work on the real robot as well as in simulation.
+
+Inspired by previous efforts in learning end-to-end control for driving using deep reinforcement learning \cite{DBLP:journals/corr/abs-1807-00412} our original plan was to evaluate a selection of reinforcement learning algorithms to solve this task.
+Knowing that reproducing reinforcement results is difficult and often unsuccessful \cite{henderson2019deep}, we planned to also experiment with a behavior cloning approach inspired by prior work from NVIDIA where a convolutional neural network was trained to steer a car using only image data \cite{DBLP:journals/corr/BojarskiTDFFGJM16}.
 
 \section{Environment Setup}
+
+We performed experimentation and evaluation of our agents in simulation and on the real robot primarily relying on the ``AI Driving Olympics" infrastructure \cite{zilly2019ai}.
+Our agent was structured into the AIDO submission format and then executed either in simulation or on the real duckiebot.
+We used the default episode length configuration, which runs agents for 60 seconds.
+
 \subsection{Simulation}
-\todo Discuss gym-duckietown and AIDO submissions
+
+We used the \texttt{gym-duckietown} simulator \cite{gym_duckietown} for training and evaluation of agents when using a reinforcement learning approach, as well as for evaluation when using behavior cloning (through the AIDO submission infrastructure).
+For reinforcement learning we only ran evaluation on the most simple map type, ``loop\_empty", which is an square map with no obstacles.
+Evaluations for behavior cloning used a specific ``challenge", \texttt{aido-LF-sim-validation} which runs the agent on a static selection of maps and ranks submissions against other users.
 
 \subsection{Real World}
-\todo Show different maps used
 
-% \begin{figure}[H]
-% \includegraphics[width=8cm,keepaspectratio]{map_simple_loop}
-% \centering
-% \caption{Photo of physical layout of map 1.}
-% \label{fig:map_simple_loop}
-% \end{figure}
+Evaluation on the real duckiebot was done on four different maps (\ref{fig:maps}), with a 60 second maximum episode duration. Only map2 was used for real robot data collection.
+
+\begin{figure}[H]
+\centering
+    \subfloat[\centering map1]{{\includegraphics[width=5cm]{map1} }}
+    \qquad
+    \subfloat[\centering map2]{{\includegraphics[width=5cm]{map2} }}
+    \qquad
+    \subfloat[\centering map3]{{\includegraphics[width=5cm]{map3} }}
+    \qquad
+    \subfloat[\centering map4]{{\includegraphics[width=5cm]{map4} }}
+    \caption{Digital overview of the four maps used for real-world evaluation.}
+    \label{fig:maps}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[angle=270,width=8cm,keepaspectratio]{map2_real}
+\centering
+\caption{Photo of physical layout of map2.}
+\label{fig:map2_real}
+\end{figure}
 
@@
 
-\todo Show training results using DQN and videos of simulator performance
+Unfortunately we were unsuccessful in achieving reasonable training results with this method, with our agent consistently showing an inability to increase average reward obtained despite experimenting with domain randomization in the simulator, training across multiple maps, and performing hyperparameter search (Figure \ref{fig:dqn_training}).
+
+\url{https://youtu.be/SDZ59_2zhGg}
 
@@
 
-\todo Show training results using DDPG and videos of simulator performance
+\url{https://youtu.be/1xL8b2MK6N4}
 
@@
 \subsection{Data Preparation}
+
 \todo Discuss data collection procedure and cleaning
+\begin{figure}[H]
+\centering
+    \subfloat[\centering Simulated data]{{\includegraphics[width=5cm]{sim_data} }}
+    \qquad
+    \subfloat[\centering Public log data]{{\includegraphics[width=5cm]{log_data} }}
+    \qquad
+    \subfloat[\centering Custom data]{{\includegraphics[width=5cm]{custom_data} }}
+    \caption{Example frames from the three different data sources used for training. Observations are downsampled 150x200 pixel RGB images.}
+    \label{fig:maps}
+\end{figure}
 
-\todo Discuss final datasets used
+Ultimately we used two final datatsets.
+The largest (henceforth ``dataset A") was used for training the initial model and consisted of 58,414 total observation frames with associated joystick controls, this was a mix of simulated data collected from \texttt{gym-duckietown} using controls given by a built-in pure pursuit controller (50,337 frames) and real robot data from (8,077 frames).
+The second dataset (henceforth ``dataset B") was compiled from ROS bags collected from one of our own robots being driven on map2 (Figure \ref{fig:maps}b) consisting of 15,560 total frames with controls provided by a human driver (11,661 frames are traveling counter-clockwise).
 
 \subsection{Model Architectures}
+
+Our experiments were focused around two model architectures, the first was an attempt to reproduce results from NVIDIA \cite{DBLP:journals/corr/BojarskiTDFFGJM16} which we named the ``nvidia" model.
+In that work the authors learn
+
+\begin{figure}
+  \centering
+  \raisebox{35pt}{\parbox[b]{.1\textwidth}{modelv0}}%
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv0_linear_accuracy}}\hfill
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv0_angular_accuracy}}\hfill
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv0_loss}}\par
+  \raisebox{35pt}{\parbox[b]{.1\textwidth}{modelv1}}%
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv1_linear_accuracy}}\hfill
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv1_angular_accuracy}}\hfill
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv1_loss}}\par
+  \raisebox{35pt}{\parbox[b]{.1\textwidth}{nvidia}}%
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{nvidia_linear_accuracy}}\hfill
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{nvidia_angular_accuracy}}\hfill
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{nvidia_loss}}
+  \caption{Results from training the three different model architectures on dataset A, showing loss, linear accuracy, and angular accuracy achieved.
+A prediction was considered correct if the continuous velocity value was within 5\% of the label value.}
+  \label{fig:training_results}
+\end{figure}
+
+% \begin{figure}[H]
+%   \centering
+%   \includegraphics[width=5cm]{modelv0_linear_accuracy}
+%   \includegraphics[width=5cm]{modelv0_angular_accuracy}
+%   \includegraphics[width=5cm]{modelv0_loss}
+
+%   \includegraphics[width=5cm]{modelv1_linear_accuracy}
+%   \includegraphics[width=5cm]{modelv1_angular_accuracy}
+%   \includegraphics[width=5cm]{modelv1_loss}
+
+%   \includegraphics[width=5cm]{nvidia_linear_accuracy}
+%   \includegraphics[width=5cm]{nvidia_angular_accuracy}
+%   \includegraphics[width=5cm]{nvidia_loss}
+% \end{figure}
+
 \todo Discuss each model architecture evaluted
@@
 
+Baselines map2:
+\url{https://youtu.be/oNrlfTRxNy0}
+
+Model v1 map2:
+\url{https://youtu.be/NMiHz7VIw_4}
+
 \section{Potential Future Improvements}

### 2021-05-29 aido_submission/v1/solution.py
added 200 epoch v1 model to solution

@@ -37,7 +37,8 @@ class Agent:
         model = Modelv1()
         model.load_state_dict(
             torch.load(
-                "modelv1_maserati_bill_simulated_amadobot_base.pth",
+                "modelv1_maserati_bill_simulated_amadobot_base_epoch_200.pth",
+                # "modelv1_maserati_bill_simulated_amadobot_base.pth",
                 # 'modelv1_maserati_plus_simulated.pth',
                 map_location=self.device,
         ))

### 2021-05-29 paper/paper.tex
Add figures for RL training, CNN model, bc overview

@@
 In this project we sought to explore methods for learning an end-to-end control policy that would allow the duckiebot to navigate tracks autonomously.
-Our goal was to enable the duckiebot and have it make a full loop around a track without any major driving infractions, using only monocular camera data.
+Our goal was to enable the duckiebot and have it navigate around an entire track without any major driving infractions (defined as exiting the lane or going off the road), using only monocular camera data.
 Ideally this system would be robust enough to generalize to new tracks and work on the real robot as well as in simulation.
@@
 We used the default episode length configuration, which runs agents for 60 seconds.
+The AIDO submission format requires structuring an agent that obeys the AIDO agent interface and accepts image observations and outputs control commands.
+We referenced the baseline implementations for both reinforcement learning and behavior cloning submission types, \url{https://github.com/duckietown/challenge-aido_LF-baseline-RL-sim-pytorch} and \url{https://github.com/duckietown/challenge-aido_LF-baseline-behavior-cloning}, respectively.
 
@@
 \section{Reinforcement Learning Approach}
-\todo Discuss our initial approach using RL
 
-\todo how we anticipated this would work
+Our initial solution was to use the \texttt{gym-duckietown} environment to train an agent using a model-free off-policy Q-learning algorithm, for which we explored both DQN \cite{DBLP:journals/corr/MnihKSGAWR13} and DDPG \cite{journals/corr/LillicrapHPHETS15} algorithms.
+Our training code leveraged pre-written implementations of both algorithms provided through the RLLib package \cite{DBLP:journals/corr/abs-1712-09381}.
+We leveraged the existing default reward function provided by the gym environment (\url{https://git.io/JGnsg}) which is a linear function of the robot speed, position within the lane relative to the right line, and proximity to obstacles.
 
-\todo ultimately how it performed poorly
+\todo Some brief amount of discussion about DQN and DDPG that shows we at least understand it \\
 
-\subsection{DQN}
-\todo Discuss general algorithmic idea behind DQN
+Unfortunately we were unsuccessful in achieving reasonable training results with this method, with our agent consistently showing an inability to increase average reward obtained despite experimenting with domain randomization in the simulator, training across multiple maps, and performing hyperparameter search (Figure \ref{fig:rl_training}).
+Our initial impression was that training an agent to perform well in simulation would be straightforward and the main challenge would be in transferring the agent to the real environment.
+When our agents failed to show any promising results during training and subsequently failed to perform in simulation at all, we decided to abandon this approach.
+Videos of evaluation of these agents in simulation can be found at \url{https://youtu.be/SDZ59_2zhGg} (DQN agent) and \url{https://youtu.be/1xL8b2MK6N4} (DDPG agent).
 
-Unfortunately we were unsuccessful in achieving reasonable training results with this method, with our agent consistently showing an inability to increase average reward obtained despite experimenting with domain randomization in the simulator, training across multiple maps, and performing hyperparameter search (Figure \ref{fig:dqn_training}).
-
-\url{https://youtu.be/SDZ59_2zhGg}
-
-\subsection{DDPG}
-\todo Discuss general algorithmic idea behind DDPG
-
-\url{https://youtu.be/1xL8b2MK6N4}
+\begin{figure}[H]
+\centering
+    \subfloat{{\includegraphics[width=7cm]{dqn_reward} }}
+    \qquad
+    \subfloat{{\includegraphics[width=7cm]{ddpg_reward} }}
+    \caption{Mean reward obtained per epoch during training of the DQN (a) and DDPG (b) solutions.
+Both solutions failed to improve mean reward.
+Here only 20 epochs are shown, but the plateau in reward obtained was observed even when trained for many more epochs.}
+    \label{fig:rl_training}
+\end{figure}
 
 \section{Behavior Cloning Approach}
-\todo High level overview of behavior cloning and end-to-end control with monocular images
+
+Our focus then shifted towards a strategy where we would train a convolutional neural network (CNN) that would accept a single camera image from the robot at each timestep and then output a prediction for the linear and angular velocity that the robot should apply.
+This approach was influenced by work from NVIDIA where this technique was applied to predicting a single value representing the steering of the vehicle \cite{DBLP:journals/corr/BojarskiTDFFGJM16}.
+We designed several CNN models (discussed in Section \ref{sec:model_arch}) and trained them on a combination of simulation and real world data, then evaluated these models using the AIDO leaderboard and on the real duckiebot.
+An high-level overview of this system is shown in Figure \ref{fig:cnn_overview}.
+
+\begin{figure}
+\includegraphics[width=8cm,keepaspectratio]{cnn_overview}
+\centering
+\caption{Overview of input training data and data flow during inference for the behavior cloning approach to end-to-end control.
+At runtime the robot passes each observation frame to the CNN model to produce predicted linear and angular velocities.
+These velocities are converted to left and right wheel velocity commands which are issued to the robot.}
+\label{fig:cnn_overview}
+\end{figure}
 
@@
 
-\todo Discuss data collection procedure and cleaning
-\begin{figure}[H]
+Data collection from simulation in the \texttt{gym-duckietown} environment is easier, faster, and less noisy than real world data, so the overall data strategy was to focus on collecting a large volume of simulated data and augmenting its applicability to real robot evaluation by including a smaller amount of real robot data extracted from ROS bags.
+
+To collect simulated data, a built-in demo was executed in the simulator that uses a pure pursuit controller \cite{DBLP:journals/corr/PadenCYYF16} to geometrically determine the optimal robot controls, the resulting image observations and joystick controls were aggregated.
+Image observations from simulation were downsampled to 150x200 and domain randomization was applied during the simulation runs to help prevent overfitting to the simulation environment.
+
+Real robot data was collected through a combination of accessing publicly available ROS bags \cite{paull17duckietown} and ROS bags recorded from demonstrations with one of our own robots on map2 (Figure \ref{fig:maps}b).
+When selecting public robot logs, we attempted to find executions which were successfully navigating the map, were free of obstacles, and contained turns.
+For the custom data robot controls were given by a human driver.
+
+% \begin{figure}[H]
+\begin{figure}
 \centering
@@
     \subfloat[\centering Custom data]{{\includegraphics[width=5cm]{custom_data} }}
-    \caption{Example frames from the three different data sources used for training. Observations are downsampled 150x200 pixel RGB images.}
-    \label{fig:maps}
+    \caption{Example frames from the three different data sources used for training. Observations are downsampled 150x200 pixel images.}
+    \label{fig:data_examples}
 \end{figure}
@@
 Ultimately we used two final datatsets.
-The largest (henceforth ``dataset A") was used for training the initial model and consisted of 58,414 total observation frames with associated joystick controls, this was a mix of simulated data collected from \texttt{gym-duckietown} using controls given by a built-in pure pursuit controller (50,337 frames) and real robot data from (8,077 frames).
-The second dataset (henceforth ``dataset B") was compiled from ROS bags collected from one of our own robots being driven on map2 (Figure \ref{fig:maps}b) consisting of 15,560 total frames with controls provided by a human driver (11,661 frames are traveling counter-clockwise).
+The largest (henceforth ``dataset A") was used for training the initial model and consisted of 58,414 total observation frames with associated controls, this was a mix of simulated data collected from \texttt{gym-duckietown} (50,337 frames) and public real robot data (8,077 frames).
+The second dataset (henceforth ``dataset B") was used for experimenting with fine tuning our models and consisted of 15,560 total frames, this only contained our custom real robot data.
 
-\subsection{Model Architectures}
+\subsection{Model Architectures} \label{sec:model_arch}
 
-Our experiments were focused around two model architectures, the first was an attempt to reproduce results from NVIDIA \cite{DBLP:journals/corr/BojarskiTDFFGJM16} which we named the ``nvidia" model.
-In that work the authors learn
+    Our experiments were focused around two model architectures, the first was an attempt to reproduce results from NVIDIA \cite{DBLP:journals/corr/BojarskiTDFFGJM16} which we named the ``nvidia" model (Figure \ref{fig:model_arch}a).
+In order to predict two values (linear and angular velocity) two separate instantiations of this model were created with disjoint weights.
+The only major deviations from the originally published model were the use of leaky rectified linear unit (LeakyReLU) activations and dropout in-between linear layers ($p=0.5$).
+    The second architecture used a smaller number of total parameters, shared weights across the convolutional layers, and two outputs preceded by small disjoint linear layers (Figure \ref{fig:model_arch}b).
+We named the initial version of this model the clever name ``modelv0", subsequent experimentation produced a second version ``modelv1" which
+
+\begin{figure}
+    \subfloat[\centering]{\includegraphics[width=.22\textwidth,keepaspectratio]{nvidia_arch}}
+    \subfloat[\centering]{\includegraphics[width=.43\textwidth,keepaspectratio]{dual_cnn_arch}}
+\centering
+\caption{}
+\label{fig:model_arch}
+\end{figure}
+
+\subsection{Training}
+All models were trained initially on the aggregated dataset (``dataset A") for 200 epochs using stochastic gradient descent and mean squared error loss.
+Results of training can be seen in Figure \ref{fig:training_results}.
 
@@
   \centering
+  \raisebox{35pt}{\parbox[b]{.1\textwidth}{nvidia}}%
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{nvidia_linear_accuracy}}\hfill
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{nvidia_angular_accuracy}}\hfill
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{nvidia_loss}}\par
   \raisebox{35pt}{\parbox[b]{.1\textwidth}{modelv0}}%
@@
   \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv1_angular_accuracy}}\hfill
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv1_loss}}\par
-  \raisebox{35pt}{\parbox[b]{.1\textwidth}{nvidia}}%
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{nvidia_linear_accuracy}}\hfill
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{nvidia_angular_accuracy}}\hfill
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{nvidia_loss}}
+  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv1_loss}}
   \caption{Results from training the three different model architectures on dataset A, showing loss, linear accuracy, and angular accuracy achieved.
@@
 
-% \begin{figure}[H]
-%   \centering
-%   \includegraphics[width=5cm]{modelv0_linear_accuracy}
-%   \includegraphics[width=5cm]{modelv0_angular_accuracy}
-%   \includegraphics[width=5cm]{modelv0_loss}
+\section{Performance Evaluations}
 
-%   \includegraphics[width=5cm]{modelv1_linear_accuracy}
-%   \includegraphics[width=5cm]{modelv1_angular_accuracy}
-%   \includegraphics[width=5cm]{modelv1_loss}
-
-%   \includegraphics[width=5cm]{nvidia_linear_accuracy}
-%   \includegraphics[width=5cm]{nvidia_angular_accuracy}
-%   \includegraphics[width=5cm]{nvidia_loss}
-% \end{figure}
-
-\todo Discuss each model architecture evaluted
-
-\todo Show data from training
-
-\section{Performance Evaluation}
 \subsection{Simulator and AIDO}

### 2021-05-29 paper/paper.tex
Add fine tuning figures

@@
 \begin{figure}[H]
-\includegraphics[angle=270,width=8cm,keepaspectratio]{map2_real}
+\includegraphics[angle=-90,width=8cm,keepaspectratio]{map2_real}
 \centering
@@
 \centering
-    \subfloat[\centering Simulated data]{{\includegraphics[width=5cm]{sim_data} }}
+    \subfloat[\centering Simulated data]{{\includegraphics[width=4cm]{sim_data} }}
     \qquad
-    \subfloat[\centering Public log data]{{\includegraphics[width=5cm]{log_data} }}
+    \subfloat[\centering Public log data]{{\includegraphics[width=4cm]{log_data} }}
     \qquad
-    \subfloat[\centering Custom data]{{\includegraphics[width=5cm]{custom_data} }}
+    \subfloat[\centering Custom data]{{\includegraphics[width=4cm]{custom_data} }}
     \caption{Example frames from the three different data sources used for training. Observations are downsampled 150x200 pixel images.}
@@
     The second architecture used a smaller number of total parameters, shared weights across the convolutional layers, and two outputs preceded by small disjoint linear layers (Figure \ref{fig:model_arch}b).
-We named the initial version of this model the clever name ``modelv0", subsequent experimentation produced a second version ``modelv1" which
+We named the initial version of this model ``modelv0", subsequent experimentation produced a second version ``modelv1" which substituted ReLU activations for LeakyReLU, and added dropout to the final linear layers ($p=0.5$) and the shared convolutional layers ($p=0.1$).
 
@@
 \centering
-\caption{}
+    \caption{Overview of the two primary model architectures evaluated in this work.
+(a) features a larger number of total parameters and no shared weights, each of the two prediction values retain their own copy of the model (b) uses shared convolutional layers and small linear layers preceding each of the two outputs.}
 \label{fig:model_arch}
@@
 \subsection{Training}
-All models were trained initially on the aggregated dataset (``dataset A") for 200 epochs using stochastic gradient descent and mean squared error loss.
-Results of training can be seen in Figure \ref{fig:training_results}.
+All training was done using stochastic gradient descent and mean squared error loss.
+The models were trained initially on the aggregated dataset (``dataset A") for 200 epochs, results in Figure \ref{fig:training_results}.
+As the ``nvidia" model did not show promising results during training, it was excluded from further experimentation.
+Then ``modelv0" and ``modelv1" were fine tuned for 50 epochs using the custom real robot dataset (``dataset B"), results in Figure \ref{fig:fine_tuning_training_results}.
 
@@
   \raisebox{35pt}{\parbox[b]{.1\textwidth}{nvidia}}%
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{nvidia_linear_accuracy}}\hfill
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{nvidia_angular_accuracy}}\hfill
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{nvidia_loss}}\par
+  \subfloat{\includegraphics[width=.28\textwidth]{nvidia_linear_accuracy}}\hfill
+  \subfloat{\includegraphics[width=.28\textwidth]{nvidia_angular_accuracy}}\hfill
+  \subfloat{\includegraphics[width=.28\textwidth]{nvidia_loss}}\par
   \raisebox{35pt}{\parbox[b]{.1\textwidth}{modelv0}}%
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv0_linear_accuracy}}\hfill
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv0_angular_accuracy}}\hfill
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv0_loss}}\par
+  \subfloat{\includegraphics[width=.28\textwidth]{modelv0_linear_accuracy}}\hfill
+  \subfloat{\includegraphics[width=.28\textwidth]{modelv0_angular_accuracy}}\hfill
+  \subfloat{\includegraphics[width=.28\textwidth]{modelv0_loss}}\par
   \raisebox{35pt}{\parbox[b]{.1\textwidth}{modelv1}}%
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv1_linear_accuracy}}\hfill
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv1_angular_accuracy}}\hfill
-  \subfloat[][]{\includegraphics[width=.28\textwidth]{modelv1_loss}}
-  \caption{Results from training the three different model architectures on dataset A, showing loss, linear accuracy, and angular accuracy achieved.
+  \subfloat{\includegraphics[width=.28\textwidth]{modelv1_linear_accuracy}}\hfill
+  \subfloat{\includegraphics[width=.28\textwidth]{modelv1_angular_accuracy}}\hfill
+  \subfloat{\includegraphics[width=.28\textwidth]{modelv1_loss}}
+  \caption{Results from training the three different model architectures on dataset A, showing linear accuracy, angular accuracy, and loss achieved.
 A prediction was considered correct if the continuous velocity value was within 5\% of the label value.}
   \label{fig:training_results}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \raisebox{35pt}{\parbox[b]{.1\textwidth}{modelv0}}%
+  \subfloat{\includegraphics[width=.28\textwidth]{modelv0_200_fine_tuned_cw_ccw_linear_accuracy}}\hfill
+  \subfloat{\includegraphics[width=.28\textwidth]{modelv0_200_fine_tuned_cw_ccw_angular_accuracy}}\hfill
+  \subfloat{\includegraphics[width=.28\textwidth]{modelv0_200_fine_tuned_cw_ccw_loss}}\par
+  \raisebox{35pt}{\parbox[b]{.1\textwidth}{modelv1}}%
+  \subfloat{\includegraphics[width=.28\textwidth]{modelv1_200_fine_tuned_cw_ccw_linear_accuracy}}\hfill
+  \subfloat{\includegraphics[width=.28\textwidth]{modelv1_200_fine_tuned_cw_ccw_angular_accuracy}}\hfill
+  \subfloat{\includegraphics[width=.28\textwidth]{modelv1_200_fine_tuned_cw_ccw_loss}}\par
+  \caption{Results from fine tuning the shared weights models on dataset B, showing linear accuracy, angular accuracy, and loss achieved.
+A prediction was considered correct if the continuous velocity value was within 5\% of the label value.}
+  \label{fig:fine_tuning_training_results}
 \end{figure}
@@
 \subsection{Simulator and AIDO}
+
+\todo 3x3 figure showing overview map trajectories from AIDO for initial 3 models on 3 maps
+% \begin{figure}
+%   \centering
+%   \raisebox{35pt}{\parbox[b]{.1\textwidth}{nvidia}}%
+%   \subfloat{\includegraphics[width=.28\textwidth]{nvidia_linear_accuracy}}\hfill
+%   \subfloat{\includegraphics[width=.28\textwidth]{nvidia_angular_accuracy}}\hfill
+%   \subfloat{\includegraphics[width=.28\textwidth]{nvidia_loss}}\par
+%   \raisebox{35pt}{\parbox[b]{.1\textwidth}{modelv0}}%
+%   \subfloat{\includegraphics[width=.28\textwidth]{modelv0_linear_accuracy}}\hfill
+%   \subfloat{\includegraphics[width=.28\textwidth]{modelv0_angular_accuracy}}\hfill
+%   \subfloat{\includegraphics[width=.28\textwidth]{modelv0_loss}}\par
+%   \raisebox{35pt}{\parbox[b]{.1\textwidth}{modelv1}}%
+%   \subfloat{\includegraphics[width=.28\textwidth]{modelv1_linear_accuracy}}\hfill
+%   \subfloat{\includegraphics[width=.28\textwidth]{modelv1_angular_accuracy}}\hfill
+%   \subfloat{\includegraphics[width=.28\textwidth]{modelv1_loss}}
+%   \caption{Results from training the three different model architectures on dataset A, showing linear accuracy, angular accuracy, and loss achieved.
+A prediction was considered correct if the continuous velocity value was within 5\% of the label value.}
+%   \label{fig:training_results}
+% \end{figure}
+
+\todo 2x3 figure showing overview map trajectories from AIDO for modelv0+v1 with fine tuning on 3 maps
+
 \todo Share links to videos from simulator and AIDO submissions

### 2021-05-31 paper/paper.tex
Finish draft

@@
 
-Evaluation on the real duckiebot was done on four different maps (\ref{fig:maps}), with a 60 second maximum episode duration. Only map2 was used for real robot data collection.
+Evaluation on the real duckiebot was done on five different maps (\ref{fig:maps}), with a 60 second maximum episode duration. Only map2 was used for training data collection.
 
@@
     \qquad
-    \subfloat[\centering map3]{{\includegraphics[width=5cm]{map3} }}
+    \subfloat[\centering map3]{{\includegraphics[angle=90,width=4cm]{map3} }}
     \qquad
-    \subfloat[\centering map4]{{\includegraphics[width=5cm]{map4} }}
-    \caption{Digital overview of the four maps used for real-world evaluation.}
+    \subfloat[\centering map4]{{\includegraphics[angle=90,width=4cm]{map4} }}
+    \qquad
+    \subfloat[\centering map5]{{\includegraphics[angle=90,width=4cm]{map5} }}
+    \qquad
+    \caption{Digital overview of the five maps used for real-world evaluation.}
     \label{fig:maps}
@@
 \begin{figure}[H]
-\includegraphics[angle=-90,width=8cm,keepaspectratio]{map2_real}
+\includegraphics[width=8cm,keepaspectratio]{map2_real}
 \centering
@@
 When our agents failed to show any promising results during training and subsequently failed to perform in simulation at all, we decided to abandon this approach.
-Videos of evaluation of these agents in simulation can be found at \url{https://youtu.be/SDZ59_2zhGg} (DQN agent) and \url{https://youtu.be/1xL8b2MK6N4} (DDPG agent).
+Videos of evaluation of these agents in simulation can be found at:
+\begin{itemize}
+    \item DQN agent: \url{https://youtu.be/SDZ59_2zhGg}
+    \item DDPG agent: \url{https://youtu.be/1xL8b2MK6N4}
+\end{itemize}
 
@@
 Then ``modelv0" and ``modelv1" were fine tuned for 50 epochs using the custom real robot dataset (``dataset B"), results in Figure \ref{fig:fine_tuning_training_results}.
+A prediction was deemed accurate if the continuous velocity value was within 5\% of the label value.
 
@@
   \caption{Results from fine tuning the shared weights models on dataset B, showing linear accuracy, angular accuracy, and loss achieved.
-A prediction was considered correct if the continuous velocity value was within 5\% of the label value.}
+A prediction was considered correct if the continuous velocity value was within 5\% of the label value.
+Poor angular accuracy was achieved and training loss on the validation set plateaued quickly.}
   \label{fig:fine_tuning_training_results}
@@
 
-\todo 3x3 figure showing overview map trajectories from AIDO for initial 3 models on 3 maps
-% \begin{figure}
-%   \centering
-%   \raisebox{35pt}{\parbox[b]{.1\textwidth}{nvidia}}%
-%   \subfloat{\includegraphics[width=.28\textwidth]{nvidia_linear_accuracy}}\hfill
-%   \subfloat{\includegraphics[width=.28\textwidth]{nvidia_angular_accuracy}}\hfill
-%   \subfloat{\includegraphics[width=.28\textwidth]{nvidia_loss}}\par
-%   \raisebox{35pt}{\parbox[b]{.1\textwidth}{modelv0}}%
-%   \subfloat{\includegraphics[width=.28\textwidth]{modelv0_linear_accuracy}}\hfill
-%   \subfloat{\includegraphics[width=.28\textwidth]{modelv0_angular_accuracy}}\hfill
-%   \subfloat{\includegraphics[width=.28\textwidth]{modelv0_loss}}\par
-%   \raisebox{35pt}{\parbox[b]{.1\textwidth}{modelv1}}%
-%   \subfloat{\includegraphics[width=.28\textwidth]{modelv1_linear_accuracy}}\hfill
-%   \subfloat{\includegraphics[width=.28\textwidth]{modelv1_angular_accuracy}}\hfill
-%   \subfloat{\includegraphics[width=.28\textwidth]{modelv1_loss}}
-%   \caption{Results from training the three different model architectures on dataset A, showing linear accuracy, angular accuracy, and loss achieved.
-A prediction was considered correct if the continuous velocity value was within 5\% of the label value.}
-%   \label{fig:training_results}
-% \end{figure}
+By writing an agent using the agent interface in the AIDO template, we were able to leverage the existing AIDO infrastructure for evaluating in simulation.
+We submitted all three of our models along with the baseline solution provided by Duckietown to the \texttt{aido-LF-sim-validation} challenge.
+This evaluates each solution across multiple runs and different maps, providing videos of robot execution in the simulator as well as overhead views of the robot trajectories.
+Visualization of the trajectories taken for all these models across three maps is shown in Figure \ref{fig:sim_results_original}.
+We noticed that our models performed roughly equivalent to the baseline solution or did worse.
 
-\todo 2x3 figure showing overview map trajectories from AIDO for modelv0+v1 with fine tuning on 3 maps
+Following additional experimentation it appeared that the high linear velocity predicted by our models did not allow for sufficient time to make turns, and in general our models had difficulties in applying enough angular velocity to make turns effectively.
+To counteract this issue we applied hard coded modifications to the predicted linear and angular velocities at each command time step, dividing the predicted velocity by 2 and multiplying the predicted angular velocity by $1.5$.
+Henceforth these manually modified models are signified as such with the suffix ``*".
+This modification significantly improved the ability of our agent to navigate, which was our primary objective, even though it was at the cost of decreased travel distance within the 60 second episode length.
+We also applied this modification to the baseline solution in order to provide a better comparison, these results can be found in Figure \ref{fig:sim_results_modified}.
 
-\todo Share links to videos from simulator and AIDO submissions
+Simulation results for the fine-tuned models were very poor, performing worse than the original unmodified models even.
+Visualizations of these results are not included for brevity, but real robot results are discussed below.
 
-\todo Discuss quantative performance for each model including baseline
+\begin{figure}
+    \centering
+    \includegraphics[width=.23\textwidth]{sim_baseline_0}
+    \includegraphics[width=.23\textwidth]{sim_nvidia_0}
+    \includegraphics[width=.23\textwidth]{sim_v0_0}
+    \includegraphics[width=.23\textwidth]{sim_v1_0}
+
+    \includegraphics[width=.23\textwidth]{sim_baseline_1}
+    \includegraphics[width=.23\textwidth]{sim_nvidia_1}
+    \includegraphics[width=.23\textwidth]{sim_v0_1}
+    \includegraphics[width=.23\textwidth]{sim_v1_1}
+
+    \subfloat[baseline]{
+        \includegraphics[width=.23\textwidth]{sim_baseline_2}
+    }
+    \subfloat[nvidia]{
+        \includegraphics[width=.23\textwidth]{sim_nvidia_2}
+    }
+    \subfloat[modelv0]{
+        \includegraphics[width=.23\textwidth]{sim_v0_2}
+    }
+    \subfloat[modelv1]{
+        \includegraphics[width=.23\textwidth]{sim_v1_2}
+    }
+    \caption{Robot trajectories in simulation on three different maps for the baseline solution (a) and each of the evaluated models (b-d).}
+  \label{fig:sim_results_original}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.23\textwidth]{sim_baseline_star_0}
+    \includegraphics[width=.23\textwidth]{sim_nvidia_star_0}
+    \includegraphics[width=.23\textwidth]{sim_v0_star_0}
+    \includegraphics[width=.23\textwidth]{sim_v1_star_0}
+
+    \includegraphics[width=.23\textwidth]{sim_baseline_star_1}
+    \includegraphics[width=.23\textwidth]{sim_nvidia_star_1}
+    \includegraphics[width=.23\textwidth]{sim_v0_star_1}
+    \includegraphics[width=.23\textwidth]{sim_v1_star_1}
+
+    \subfloat[baseline*]{
+        \includegraphics[width=.23\textwidth]{sim_baseline_star_2}
+    }
+    \subfloat[nvidia*]{
+        \includegraphics[width=.23\textwidth]{sim_nvidia_star_2}
+    }
+    \subfloat[modelv0*]{
+        \includegraphics[width=.23\textwidth]{sim_v0_star_2}
+    }
+    \subfloat[modelv1*]{
+        \includegraphics[width=.23\textwidth]{sim_v1_star_2}
+    }
+    \caption{Robot trajectories in simulation on three different maps for the baseline solution (a) and each of the evaluated models (b-d), in all cases the solutions were manually modified to apply a linear transformation of the predicted velocity values.}
+  \label{fig:sim_results_modified}
+\end{figure}
 
@@
 
-\todo Discuss quantative performance for each model including baseline
+Having previously determined in simulation that the manually modified models (``nvidia*", ``modelv0*", ``modelv1*") performed best, we expected this result to be true during real robot evaluation as well.
+All initial evaluations were done on map2 (Figure \ref{fig:maps}b) and from these we determined that ``modelv1*" was the overall best performing model, so it was evaluated on the other maps as well.
 
-\todo Share links to videos for each map/model evaluated
+The following videos contain results from testing all three models along with the baseline solution on map2:
+\begin{itemize}
+    \item original models: \url{https://youtu.be/j7rHbaK74h8}
+    \item modified models: \url{https://youtu.be/6s80amO3GV8}
+\end{itemize}
 
-Baselines map2:
-\url{https://youtu.be/oNrlfTRxNy0}
+\subsubsection{Fine Tuning}
 
-Model v1 map2:
-\url{https://youtu.be/NMiHz7VIw_4}
+Consistent with the accuracy obtained during training and lack of ability to decrease validation set loss when performing fine tuning (Figure \ref{fig:fine_tuning_training_results}), real robot performance was much worse with this additional training, see \url{https://youtu.be/v5AOjATDAyU}.
+This is not altogether surprising though given that poor quality of the human driver controls used to create the custom dataset.
+It was simply too difficult to drive the robot even as a human given the coarse grained tools provided for user input and the overall quality and reliability of the robot.
+During human driving there were consistently moments where the robot seemed to drift off and execute some control the human did not apply.
+These factors likely contributed to a noisy dataset that did not improve the performance of our system.
+
+\subsubsection{Generalization}
+
+In order to evaluate the ability of our best performing model ``modelv1*" to generalize to other maps it was tested alongside ``baseline*" on the remaining maps (see below).
+In general the results were consistent with performance on map2 with the caveat that our solution could not handle right turns.
+This is likely an issue with our dataset having not enough examples of right turns and hence the robot was unable to use prior examples to successfully navigate this situation.
+
+\begin{itemize}
+    \item map1: \url{https://youtu.be/jYgHov8mpX4}
+    \item map3: \url{https://youtu.be/ALZrHWevRJ4}
+    \item map4: \url{https://youtu.be/Oodr0QcEKJM}
+    \item map5: \url{https://youtu.be/zt69aAOWHX4}
+\end{itemize}
 
 \section{Potential Future Improvements}
-
-\todo Discuss algorithmic enhancements
-
-\todo Discuss robot limitations
+\begin{enumerate}
+    \item As explained in prior sections, one limitation faced was the difficultly in collecting good real robot data.
+Possibly one way to have circumvented this was to use the duckiebot's Xbox controller interface for human driving, assuming that this input possibly has better fine grained control.
+    \item As observed in our agent's inability to generalize to certain maps, we had a dearth of data with right hand turns.
+Improving our dataset to include more diverse situations would likely improve real world performance.
+    \item In general issues with the robot caused limitations in our groups ability to properly evaluate our agents.
+One group member's robot had consistent issues with keeping its wheel on and rendered him unable to use his robot in a meaningful way.
+The use of more robust robot components would certainly improve the ability to iterate during experimentation and also have a system less subject to control noise.
+    \item We suspected that performance at inference time might have been a bottleneck for our system.
+Possibly this is one reason that introducing a hard coded linear velocity reduction improved performance, by allowing time to do inference on observations corresponding to turn taking.
+A potential place to look for performance improvement would be to either quantize our PyTorch model to speed up CPU-based inference, or to adapted our system to use the onboard GPU on the Jetson Nano.
+Despite some effort in trying to adapt the duckietown software stack to use the GPU, the containerized software system was unable to detect the on-board GPU and hence we could not leverage it.
+    \item We also believe that using a recurrent network model has the potential to improve performance.
+Although our data input is actually video, we treated it as isolated image frames and lost the ability to leverage prior observations in making predictions.
+\end{enumerate}
 

### 2021-05-31 paper/paper.tex
Added short explanation of RL algorithms

@@
 
-\newcommand\todo{\textcolor{red}{\textbf{[TODO:] }}}
+\newcommand\todo[1]{\textcolor{red}{\textbf{[TODO: #1]}}}
 
@@
 
-\todo Some brief amount of discussion about DQN and DDPG that shows we at least understand it \\
+Our first approach was DQN.
+In this case actor is learning the Q function (value function of state, action pair).
+In our case the network is given an image from the camera and is predicting the value over 3 possible actions, driving $45^\circ$ to the left/right, and driving forward.
+During training DQN averages the reward function over the whole episode.
+These episodes are then played and collected into \textit{replay buffer}, which when full triggers an iteration of neural network training.
 
-Unfortunately we were unsuccessful in achieving reasonable training results with this method, with our agent consistently showing an inability to increase average reward obtained despite experimenting with domain randomization in the simulator, training across multiple maps, and performing hyperparameter search (Figure \ref{fig:rl_training}).
+Given enough training samples (our longest run was $>200$ iterations, around 30 episodes each), the model should converge to a good result.
+Our main motivation for this network was that small set of discrete actions should overfit less to the simulation environment (this is because with slight changes to exact values of Q function calculated the maximal action would stay the same).
+However it has the obvious drawback of being much less flexible in its actions and possible recovery.
+
+Our second approach was DDPG, which by working with continuous space addresses the main drawback of DQN, as stated above, while being extremely similar.
+The main two differences lie in the fact that DDPG uses actor-critic framework, where neural network outputs both the action and the predicted value function of state input and action tuple, as well as that the fact that weights of the network are using "soft" target, which causes them to change less and stabilizes learning.
+
+\todo{Put architectures of models for DQN and DDPG here}
+
+Unfortunately we were unsuccessful in achieving reasonable training results with these methods, with our agent consistently showing an inability to increase average reward obtained despite experimenting with domain randomization in the simulator, training across multiple maps, and performing hyperparameter search (Figure \ref{fig:rl_training}).
 Our initial impression was that training an agent to perform well in simulation would be straightforward and the main challenge would be in transferring the agent to the real environment.
+We tried customizing reward function to additionally benefit from distance travelled, but to no fruition.
 When our agents failed to show any promising results during training and subsequently failed to perform in simulation at all, we decided to abandon this approach.

### 2021-06-01 data_converter/src/extract_data.py
Added per-episode extraction

@@ -19,7 +19,7 @@ VEHICLE_NAME = 'maserati'
 MessageCollection = collections.namedtuple(
     "MessageCollection", ["topic", "type", "messages"])
 
-frank_logger = Logger(log_file='converted/dataset.log')
+frank_logger = Logger(log_file=f'converted/{VEHICLE_NAME}')
 
 
 def extract_messages(path, requested_topics):
@@ -31,17 +31,12 @@ def extract_messages(path, requested_topics):
     bag = rosbag.Bag(path)
 
     _, available_topics = bag.get_type_and_topic_info()
-
-    # print(available_topics)
-
     # check if the requested topics exist in bag's topics and if yes extract the messages only for them
     extracted_messages = {}
     for topic in requested_topics:
-        if topic not in available_topics:
-            raise ValueError(
-                "Could not find the requested topic (%s) in the bag %s" % (topic, path))
-        extracted_messages[topic] = MessageCollection(
-            topic=topic, type=available_topics[topic].msg_type, messages=[])
+        if topic in available_topics:
+            extracted_messages[topic] = MessageCollection(
+                topic=topic, type=available_topics[topic].msg_type, messages=[])
 
     for msg in bag.read_messages():
         topic = msg.topic
@@ -100,6 +95,8 @@ def main():
         print("Extract data for {} file.".format(file))
         try:
             msgs = extract_messages(abs_path, ros_topics_temp)
+            if not msgs:
+                continue
         except rosbag.bag.ROSBagException:
             print("Failed to open {}".format(abs_path))
             continue
@@ -117,8 +114,29 @@ def main():
                           "/camera_node/image/compressed"].messages
         ext_car_cmds = msgs["/" + duckiebot_name + "/joy"].messages
 
+        img_start_timestamp = ext_images[0].timestamp.secs + ext_images[0].timestamp.nsecs * \
+            10 ** -len(str(ext_images[0].timestamp.nsecs))
+        img_end_timestamp = ext_images[-1].timestamp.secs + ext_images[-1].timestamp.nsecs * \
+            10 ** -len(str(ext_images[-1].timestamp.nsecs))
+        control_start_timestamp = ext_car_cmds[0].timestamp.secs + ext_car_cmds[0].timestamp.nsecs * \
+            10 ** -len(str(ext_car_cmds[0].timestamp.nsecs))
+        control_end_timestamp = ext_car_cmds[-1].timestamp.secs + ext_car_cmds[-1].timestamp.nsecs * \
[…]

### 2021-06-07 paper/paper.tex

@@
 The main two differences lie in the fact that DDPG uses actor-critic framework, where neural network outputs both the action and the predicted value function of state input and action tuple, as well as that the fact that weights of the network are using "soft" target, which causes them to change less and stabilizes learning.
-
-\todo{Put architectures of models for DQN and DDPG here}
 
@@
 
+\subsection{3D Convolutions}
+To at least partially address the fifth potential improvement we decided to try 3D Convolution, where the additional dimension of kernel was over time.
+
+Different approach requires different data processing.
+We first split processed each log separately into episodes.
+For sentence length $S = 128$, we pad the first frame $S$ times to the beginning of each episode in training data.
+This is done to force robot to learn how to start driving.
+Then we iterate over these frames with step 10 creating videos of length $S$ at each step.
+For each video we define the target angular and linear velocities based on the last frame.
+Thus each observation was $\mathbb{R}^{n \times 128 \times 3 \times 150 \times 200}$ (where $n$ is batch size), while both velocities were $\mathbb{R}$.
+Lastly, since angular velocities are skewed significantly towards $0^\circ$ training data is filtered so that there are equal amounts of examples with $|\omega| > 0.25$ and $|\omega| \le 0.25$.
+
+Model architecture uses multiple 3D convolution layers with decreasing number of channels (time dimension) from 128 to 16.
+Model then reshapes data to $\mathbb{R}^{n \times 48 \times 150 \times 200}$ and passes it through architecture similar to V1.
+
+\begin{figure}
+\centering
+    \subfloat[\centering Linear Accuracy]{{\includegraphics[width=0.4\textwidth]{figures/model3d_linear_accuracy.png} }}
+    \qquad
+    \subfloat[\centering Angular Accuracy]{{\includegraphics[width=0.4\textwidth]{figures/model3d_angular_accuracy.png} }}
+    \caption{Results from training model with 3D convolutions.}
+    \label{fig:data_examples}
+\end{figure}
+
+The results of the model were disappointing, as it failed to successfully predict almost any angular velocity correctly.
+Moreover it also overfitted to training data, while performing worse than all image based models.
+
+In conclusion we believe that video-based inference is a viable approach, however 3D convolutions are not the best suited for the task, or are extremely difficult to find correct hyperparameters for.
 \bibliographystyle{alpha}

### 2021-06-07 paper/paper.tex
Clarify that we are lane following

@@
 \usepackage[utf8]{inputenc}
-\usepackage{amsmath, enumitem, url}
+\usepackage{amsmath, enumitem, url, amsfonts}
 \usepackage{xcolor}
@@
 In this project we sought to explore methods for learning an end-to-end control policy that would allow the duckiebot to navigate tracks autonomously.
-Our goal was to enable the duckiebot and have it navigate around an entire track without any major driving infractions (defined as exiting the lane or going off the road), using only monocular camera data.
+Our goal was to enable the duckiebot and have it follow a lane and navigate around an entire track without any major driving infractions (defined as exiting the lane or going off the road), using only monocular camera data.
 Ideally this system would be robust enough to generalize to new tracks and work on the real robot as well as in simulation.
